---
title: "Trex 1402 Upsetplot"
author: "Sandra de Haan"
date: "2024-02-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
'

```{r}
library(UpSetR)
library(Seurat)
library(dplyr)
library(ggplot2)
library(patchwork)
library(circlize)
```

```{r}
Meta1402 <- as.data.frame(Trex_mt10dim40_SCT_clone_sub2_5@meta.data)
```

```{r}
Meta1402
```


```{r}
cells_per_clone <- Meta1402 %>%
  group_by(cloneID1402) %>%
summarise(number_of_cells = n())
```


```{r}
write.csv(cells_per_clone, file = "cells_per_clone2802.csv")
```

```{r}
clones_2_and_more <- cells_per_clone%>%
  filter(number_of_cells >1)%>%
  filter(cloneID1402!= "0")
```

```{r}
write.csv(clones_2_and_more, file = "clones_2_and_more2802.csv")
```


```{r}
cells_per_clone
```


```{r}
clones_2_and_more
```




For Upsetplot
```{r}
clones_2_and_more<- clones_2_and_more$cloneID1402
```




```{r}
# extract results for selected cloneIDs

# helper data frames
loop_results <- data.frame()
step_result <- data.frame()

# loop
for (i in clones_2_and_more) {
  step_result <- filter(Meta1402, cloneID1402 == i)
  loop_results <- bind_rows(loop_results, step_result)
}

clone_analysis <- loop_results
```

```{r}

clone_analysis <- left_join(clone_analysis, cells_per_clone, by = "cloneID1402")
```

```{r}
head(clone_analysis)
```

```{r}
write.csv(clone_analysis, file = "clone_analysis.csv")
```



```{r}
colnames(clone_analysis)[48] <- "clone_size"
```

```{r}
for_upset <- clone_analysis%>%
  select("subclusters_2509", "cloneID1402", "clone_size", "cellID")
```

```{r}
for_upset$value <- rep(1, 8826)

upset <- tidyr::pivot_wider(for_upset, names_from = subclusters_2509, 
                   values_from = value)

# replace NAs with 0
upset[is.na(upset)] <- 0
```


```{r}
write.csv(upset, file = "Upset_Trex2802.csv")
```


```{r}
Upset_input <- read.csv("upset2802.csv", sep = ";")
```

```{r}
Upset_input2205 <- read.csv("upset2802_noMP_noglia.csv", sep = ";")
```


```{r}
Upset_sel <- read.csv("upsetselection2005.csv", sep = ";")
```


```{r}
Upset_origin <- read.csv("upset2802embryo.csv", sep = ";")
```

```{r}
Upset_SGNcom <- read.csv("Upset_input1802SGNcombined.csv", sep = ";")
```


```{r}
Upset_origin
```


```{r}
Upset_input
```


```{r}
library(UpSetR)
```


```{r}
Upsetplot2802 <-upset(Upset_input, nsets = 5500, nintersects = 81, order.by = "freq", mb.ratio = c(0.5, 0.5), matrix.color = "darkred", main.bar.color = "black", sets.bar.color = "black", keep.order = T, sets = c("Cluster19", "Cluster3", "Cluster4", "Cluster5", "Cluster6", "Cluster7", "Cluster40", "Cluster8", "Cluster50", "Cluster0", "Cluster2", "Cluster1", "Cluster25", "Cluster9", "Cluster18", "Cluster24", "Cluster30", "Cluster11", "Cluster23", "Cluster17", "Cluster10", "Cluster16", "Cluster22"))
```

"Cluster22", "Cluster16", "Cluster10", "Cluster17", "Cluster23", "Cluster11", "Cluster30", "Cluster24", "Cluster18", "Cluster9", "Cluster25", "Cluster1", "Cluster2", "Cluster0"

#selection of only 2 or more co-occurances
```{r}
Upsetplot2802 <-upset(Upset_input, nsets = 5500, nintersects = 81, order.by = "freq", mb.ratio = c(0.5, 0.5), matrix.color = "black", main.bar.color = "black", sets.bar.color = "black", keep.order = T, sets = c("Cluster19", "Cluster3", "Cluster4", "Cluster5", "Cluster6", "Cluster7", "Cluster40", "Cluster22", "Cluster16", "Cluster10", "Cluster17", "Cluster23", "Cluster11", "Cluster30", "Cluster24", "Cluster18", "Cluster9", "Cluster25", "Cluster1", "Cluster2", "Cluster0", "Cluster50", "Cluster8"))
```

#all co-occurances 
```{r}
Upsetplot2802 <-upset(Upset_input, nsets = 5500, nintersects = 5000, order.by = "freq", mb.ratio = c(0.5, 0.5), matrix.color = "black", main.bar.color = "black", sets.bar.color = "black", keep.order = T, sets = c("Cluster19", "Cluster3", "Cluster4", "Cluster5", "Cluster6","Cluster40", "Cluster7", "Cluster22", "Cluster16", "Cluster10", "Cluster17", "Cluster23", "Cluster11", "Cluster30", "Cluster24", "Cluster18", "Cluster9", "Cluster25", "Cluster1", "Cluster2", "Cluster0", "Cluster50", "Cluster8"))
```



Combinations of cluster
```{r}
Upset_input %>%
  filter(Cluster40==1)%>%
  filter(Cluster50==1)
```



```{r}
Upset_input%>%
 filter(Cluster0!=1)%>%
filter(Cluster1!=1)%>%
filter(Cluster2!=1)%>%
filter(Cluster3!=1)%>%
filter(Cluster4!=1)%>%
filter(Cluster5!=1)%>%
filter(Cluster6!=1)%>%
filter(Cluster7!=1)%>%
filter(Cluster8!=1)%>%
filter(Cluster9!=1)%>%
filter(Cluster10!=1)%>%
filter(Cluster11!=1)%>%
filter(Cluster16!=1)%>%
filter(Cluster17!=1)%>%
filter(Cluster18!=1)%>%
filter(Cluster19!=1)%>%
filter(Cluster22!=1)%>%
filter(Cluster23!=1)%>%
filter(Cluster24!=1)%>%
filter(Cluster25!=1)%>%
filter(Cluster30!=1)%>%
filter(Cluster40!=1)%>%
filter(Cluster50==1)


```


```{r}
Circos2802 <- read.csv("Circos2802.csv", sep = ";")
```

```{r}
Circos28025ormore <- read.csv("Circos28025ormore.csv", sep = ";")
```
```{r}
Circos2802morethan5 <- read.csv("Circos2802morethan52205.csv", sep = ";")
```


```{r}
Circos1802 <- read.csv("Circos1802.csv", sep = ";")
```

```{r}
Circos1802_umaporder <- read.csv("Circos1802_umaporder.csv", sep = ";")
```

```{r}
Circos1802_umaporder5ormore <- read.csv("Circos1802_umaporder5ormore.csv", sep = ";")
```


```{r}
Circos2802OHConly <- read.csv("Circos2802OHConly.csv", sep = ";")
```

```{r}
chordDiagram(Circos2802OHConly)
```



"#FFEA00", "#FDDA0D","#DAA520", "#DAA520", "#FDDA0D", "#F4C430", "#E4D00A" 
```{r}
"#FFEA00", "#FDDA0D","#DAA520", "#DAA520", "#FDDA0D", "#F4C430", "#E4D00A"
```





```{r}
chordDiagram(Circos2802morethan5, grid.col = c("#0096FF",  "#89CFF0", "#7393B3", "#6495ED", "#0047AB","#FFAC1C", "#CC5500", "#009E60", "#097969", "#50C878", "#4F7942", "#A12BAA", "#9B6F9E", "#9B6F9E80", "#FDDA0D", "#DAA520", "#E4D00A",  "#E0115F", "#E97451", "#AA4A44", 	"#E34234", "#E3735E", "black"))
```
```{r}
chordDiagram(Circos2802)
```



```{r}
chordDiagram(Circos2802morethan5, grid.col = c("#FFAC1C",  "#FFAC1C", "#FFAC1C", "#FFAC1C", "#FFAC1C", "#FFAC1C","#FFAC1C", "#FFAC1C", "#FFAC1C", "#FFAC1C", "#FFAC1C", "#FFAC1C", "#FFAC1C", "#FFAC1C",  "#89CFF0","#FFAC1C", "#FFAC1C",  "#FFAC1C", "#89CFF0", "#89CFF0", 	"#89CFF0", "#89CFF0", "black"))
```


```{r}
meta1902<- as.data.frame(Trex_mt10dim40_SCT_clone_sub2_5@meta.data)
```


```{r}
meta1902
```


Umaps with barcode information

```{r}
FeaturePlot(Trex_mt10dim40_SCT_clone_sub2_5, features = c("Tomato-N"), order = TRUE, cols = c("lightgrey", "#3d85c6"))
```
```{r}
DefaultAssay(Trex_mt10dim40_SCT_clone_sub2_5) <- "SCT"
```

--

```{r}
Tomato_expression = GetAssayData(object = Trex_mt10dim40_SCT_clone_sub2_5, assay = "RNA", slot = "data")["Tomato-N",]

head(Tomato_expression,30)
```

```{r}
pos_ids = names(which(Tomato_expression>0))
```

```{r}
pos_ids
```


```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, cells.highlight = pos_ids, cols.highlight = c("#3d85c6"))
```



```{r}
Idents(Trex_mt10dim40_SCT_clone_sub2_5) <- "subclusters_2509"
```

```{r}
Idents(Trex_mt10dim40_SCT_clone_sub2_5) <- "cloneID1402"
```


```{r}
CloneIDpos <- meta_check%>%
  filter(cloneID1402>0)%>%
  filter(number_of_cells>1)%>%
  select(cellID)
```


```{r}
CloneIDpos
```



```{r}
CloneIDpos_vector <- CloneIDpos$cellID
```

```{r}
CloneIDpos
```


```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, reduction = "umap", cells.highlight = CloneIDpos_vector,
        cols.highlight = "#f78917", pt.size = 2, sizes.highlight = 2)
```

```{r}
clone_analysis
```


```{r}
Multicell <- clone_analysis%>%
  filter(number_of_cells>1)%>%
  filter(cloneID1402!=0)%>%
  select(cellID)
```


```{r}
Multicell_vector <- Multicell$cellID
```

```{r}
Multicell
```


```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, reduction = "umap", cells.highlight = Multicell_vector,
        cols.highlight = "#f78917", pt.size = 2, sizes.highlight = 2)
```

cells per cloneID1402

df1 = cellID and cloneID1402

df2 = cloneID1402 and cellsperclone

should be merged so that each cellID, has a cloneID and the size of that cloneID. 
That info should be added to the Trex object

```{r}
df1 <- read.csv("df1_cellID_cloneID1402.csv", sep = ";")
```

```{r}
df2 <- read.csv("cells_per_clone1402.csv")
```


```{r}
df1
```


```{r}
dfx<- merge(df1, df2, by = "cloneID1402", all.x = TRUE)

# Check the merged DataFrame
print(dfx)
```


```{r}
df <- data.frame(cellID = rownames(Trex_mt10dim40_SCT_clone_sub2_5@meta.data), cloneID1402size= 0)
```


```{r}
matched.df <- dplyr::left_join(df,dfx, by = "cellID")

head(matched.df, 5)
```

```{r}
meta1902 <- as.data.frame(Trex_mt10dim40_SCT_clone_sub2_5@meta.data)
```

```{r}
meta1902
```


```{r}
library(dplyr)

matched.df <- matched.df %>% replace(., is.na(.), "0")
length(which(matched.df$number_of_cells > 0))

head(matched.df, 5)
```

```{r}
rownames(matched.df) <- matched.df$cellID


```


```{r}
matched.df
```


```{r}
Trex_mt10dim40_SCT_clone_sub2_5<- AddMetaData(Trex_mt10dim40_SCT_clone_sub2_5, matched.df)

```

```{r}
meta_check <- as.data.frame(Trex_mt10dim40_SCT_clone_sub2_5@meta.data)
```

```{r}
meta_check
```

```{r}
colnames(meta_check)[45] <- "CloneID1402_size"
```


```{r}
meta_check
```


```{r}
numberofbarcodes <- read.csv("numberofbarcodes.csv", sep = ";")
```

```{r}
numberofbarcodes
```


```{r}
df <- data.frame(cellID = rownames(Trex_mt10dim40_SCT_clone_sub2_5@meta.data), barcodes1402= 0)
```


```{r}
matched.df <- dplyr::left_join(df,numberofbarcodes, by = "cellID")

head(matched.df, 5)
```


```{r}
library(dplyr)

matched.df <- matched.df %>% replace(., is.na(.), "0")
length(which(matched.df$barcodes1402.y > 0))

head(matched.df, 5)
```


```{r}

rownames(matched.df) <- matched.df$cellID


```


```{r}
matched.df
```


```{r}
Trex_mt10dim40_SCT_clone_sub2_5<- AddMetaData(Trex_mt10dim40_SCT_clone_sub2_5, matched.df)
```

```{r}
meta_check <- as.data.frame(Trex_mt10dim40_SCT_clone_sub2_5@meta.data)
```

```{r}
meta_check
```
```{r}
Idents(Trex_mt10dim40_SCT_clone_sub2_5) <- "barcodes1402.y"
```

```{r}
barcode1 <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("1"))
barcode2 <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("2"))
barcode3 <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("3"))
barcode4 <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("4"))
barcode5 <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("5"))
```



```{r}
list_barcodes <- list("1" = barcode1, "2" = barcode2, "3" = barcode3, "4" = barcode4, "5" = barcode5 )
```

```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, cells.highlight = list_barcodes, order = TRUE, cols.highlight = c("#D22B2B80", "#9F2B6880", "#FFEA0080", "#FFAC1C80", "#6495ED80"))
```

```{r}
saveRDS(Trex_mt10dim40_SCT_clone_sub2_5, file = "Trex_mt10dim40_SCT_clone_sub2_5.RDS")
```


Hierachical clustering of circos plot 

```{r}
library(circlize)

install.packages("dendextend")
library(dendextend)
```

```{r}
# Sample data
set.seed(123)
data <- matrix(rnorm(100), nrow = 10)  # Creating a random matrix of 10 rows and 10 columns

# Perform hierarchical clustering
hc <- hclust(dist(data))

# Plot dendrogram
plot(hc, main = "Hierarchical Clustering Dendrogram", xlab = "Samples")

```
```{r}
data
```
```{r}
library(reshape2)
```


```{r}
matrix_data <- acast(CircosBase, from ~ to, value.var = "value", fill = 0)
hc <- hclust(dist(matrix_data))
plot(hc, main = "Hierarchical Clustering Dendrogram", xlab = "Nodes")
```
```{r}
# Perform hierarchical clustering using complete linkage
hc_complete <- hclust(dist(matrix_data), method = "complete")

# Perform hierarchical clustering using single linkage
hc_single <- hclust(dist(matrix_data), method = "single")

# Perform hierarchical clustering using average linkage
hc_average <- hclust(dist(matrix_data), method = "average")

# Perform hierarchical clustering using Ward's method
hc_ward <- hclust(dist(matrix_data), method = "ward.D")

```

```{r}
plot(hc_average)
```
 --
 
 
Highlight cloneIDs into Umap 
 
```{r}
meta2002 <- as.data.frame(Trex_mt10dim40_SCT_clone_sub2_5@meta.data)
```
 
```{r}
meta2002
```

```{r}
write.csv(meta2002, file = "meta2002.csv")
```

```{r}
Idents(Trex_mt10dim40_SCT_clone_sub2_5) <- "cloneID1402"
```


```{r}
HeCclones <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("94", "173", "278", "331", "346", "433", "494", "505", "513", "538", "542", "543", "547", "556", "717", "728", "762", "794", "802", "814", "817", "845", "872", "894", "1039", "1060", "1073", "1100", "1103", "1125", "1193", "1289", "1368", "1375", "1385", "1386", "1388", "1400", "1413", "1497", "1515", "1517", "1522", "1531", "1584", "1613", "1616", "1627", "1683", "1700", "1739", "1740", "1755", "1757", "1759", "1884", "1903", "1935", "1939", "1946", "1978", "1984", "1996", "2008", "2030", "2069", "2074", "2312", "2356"))

```

1204

```{r}
Trex_mt10dim40_SCT_clone_sub2_5$cloneID1402
```


```{r}
Idents(Trex_mt10dim40_SCT_clone_sub2_5) <- "cloneID1402"
```


```{r}
HCclones <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("434", "451", "452", "458", "473", "538", "547", "550", "652", "673", "720", "750", "788", "795", "885", "889", "993", "1087", "1100", "1189", "1254", "1296", "1340", "1356", "1380", "1402", "1408", "1487", "1492", "1554", "1568", "1575", "1613", "1627", "1632", "1683", "1716", "1733", "1848", "1880", "1893", "1917", "1945", "1984", "1994", "2016", "2074", "2087", "2164", "2214", "2236", "2285", "2319", "2368", "434", "451", "458", "473", "538", "547", "550", "720", "750", "795", "885", "889", "1087", "1100", "1254", "1296", "1340", "1380", "1408", "1487", "1568", "1613", "1683", "1848", "1880", "1945", "1984", "2016", "2074", "2087", "2236", "2368", "544", "17", "90", "139", "222", "331", "417", "433", "443", "469", "476", "477", "484", "486", "493", "499", "505", "511", "513", "524", "532", "534", "543", "556", "665", "695", "708", "728", "757", "762", "776", "784", "801", "802", "811", "814", "821", "833", "853", "864", "879", "896", "920", "958", "960", "974", "984", "1037", "1039", "1054", "1073", "1103", "1125", "1135", "1145", "1160", "1193", "1295", "1299", "1302", "1307", "1331", "1354", "1366", "1375", "1382", "1384", "1387", "1399", "1400", "1416", "1497", "1511", "1517", "1528", "1531", "1561", "1571", "1597", "1599", "1616", "1646", "1695", "1696", "1700", "1739", "1740", "1748", "1755", "1757", "1767", "1857", "1878", "1882", "1884", "1903", "1922", "1926", "1928", "1935", "1940", "1960", "1978", "2007", "2008", "2014", "2020", "2029", "2030", "2031", "2053", "2062", "2080", "2082", "2190", "2224", "2232", "2244", "2245", "2246", "2273", "2286", "2307", "2312", "2363", "2367"))

```

```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, cells.highlight = HCclones)
```


```{r}
HCclones <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("547", "433", "1125", "513", "889", "1039", "1100", "556", "1193", "511", "534", "811", "833", "879", "896", "1354", "720", "1340", "885", "1296", "17", "90", "434", "524", "535", "539", "544", "545", "645", "695", "814", "818", "849", "920", "958", "960", "984", "991", "1037", "1045", "1054", "1073", "1078", "1088", "1103", "1135", "1284", "1295", "1297", "1302", "1307", "1311", "1370", "1382", "1387", "1444", "1531", "652", "1087", "1189", "1285", "1380", "1402", "1410"))

```

```{r}
rootclones <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("12", "18", "38", "40", "46", "57", "64", "71", "81", "82", "104", "107", "108", "114", "117", "121", "123", "137", "142", "143", "154", "185", "197", "198", "199", "201", "202", "215", "222", "226", "242", "252", "257", "260", "266", "274", "275", "277", "286", "306", "319", "325", "327", "336", "343", "350", "351", "356", "357", "358", "359", "410", "415", "417", "434", "443", "444", "452", "455", "456", "465", "467", "468", "469", "470", "471", "472", "484", "499", "503", "504", "505", "513", "514", "529", "531", "532", "538", "547", "548", "550", "551", "556", "557", "559", "628", "644", "729", "741", "773", "842", "884", "935", "1017", "1071", "1102", "1110", "1126", "1156", "1158", "1201", "1228", "1237", "1246", "1292", "1293", "1296", "1341", "1343", "1353", "1366", "1379", "1397", "1400", "1401", "1402", "1414", "1426", "1443", "1446", "1454", "1455", "1475", "1480", "1515", "1517", "1519", "1522", "1531", "1537", "1542", "1543", "1565", "1571", "1577", "1578", "1584", "1587", "1610", "1613", "1616", "1617", "1636", "1640", "1647", "1652", "1653", "1669", "1700", "1740", "1754", "1755", "1757", "1759", "1765", "1767", "1804", "1808", "1821", "1870", "1874", "1884", "1893", "1914", "1929", "1935", "1943", "1949", "1961", "1962", "1976", "2008", "2009", "2019", "2020", "2023", "2042", "2046", "2055", "2066", "2067", "2100", "2113", "2132", "2133", "2224", "2228", "2236", "2244", "2245", "2250", "2251", "2252", "2302", "2312", "2360", "2362", "2363", "2368"))

```



```{r}
HCclones
```

```{r}
HeCclones
```


```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, cells.highlight = HeCclones, cols.highlight = "#A12BAA", pt.size = 2, sizes.highlight = 2)
```

```{r}
SVm <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("544", "521", "1052", "1397", "1451"))
svI <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("1377", "1428", "259", "1262", "1319", "270", "80", "110", "170", "244", "341", "424", "508", "622", "660", "744", "826", "832", "952", "1022", "1041", "1109", "1122", "1234", "1317", "1318", "1327", "1423", "1442"))
```

```{r}
SVm<- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents =c("544", "450", "316", "798", "101", "529", "2142", "2107", "475", "558", "1530", "1678", "1764", "1861", "2120", "239", "463", "521", "1397", "1694", "1914"))
```

```{r}
svI <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents =c("102", "161", "212", "259", "270", "308", "423", "424", "464", "481", "482", "491", "495", "496", "500", "509", "510", "660", "789", "952", "1109", "1247", "1262", "1264", "1275", "1317", "1319", "1352", "1377", "1415", "1428", "1442", "1463", "1465", "1538", "1539", "1595", "1604", "1626", "1631", "1658", "1675", "1888", "1889", "1890", "1918", "1963", "1980", "1997", "2036", "2039", "2065", "2116", "2147", "2158", "2162", "2187", "2226", "2231", "2263", "2300", "2317"))

```
```{r}
svI
```



```{r}
svI
```


```{r}
list_barcodes <- list("SV-M" = SVm, "SV-I" = svI)
```

```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, cells.highlight = list_barcodes, cols.highlight =c("#3d85c6", "darkblue") , pt.size = 2, sizes.highlight = 2)
```
```{r}
HeCclones <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("538", "547", "1100", "1613", "1683", "1984", "2074", "331", "433", "505", "513", "543", "556", "728", "762", "802", "814", "1039", "1073", "1103", "1125", "1193", "1375", "1400", "1497", "1517", "1531", "1616", "1700", "1739", "1740", "1755", "1757", "1884", "1903", "1935", "1978", "2008", "2030", "2312", "1627", "173", "494", "542", "717", "794", "872", "1385", "1515", "1522", "1584", "1759", "1939", "1996", "2069", "2356")
)
```

```{r}
HeCclones
```
"#f78917" 

```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, cells.highlight = HeCclones, cols.highlight = "#008000", pt.size = 2, sizes.highlight = 2)
```
```{r}
rootclones <- WhichCells(Trex_mt10dim40_SCT_clone_sub2_5, idents = c("538", "547", "1613", "505", "513", "556", "1400", "1517", "1531", "1616", "1700", "1740", "1755", "1757", "1884", "1935", "2008", "2312", "1515", "1522", "1584", "1759", "529", "1397", "1914", "434", "550", "1296", "2236", "2368", "222", "417", "443", "469", "484", "499", "532", "1366", "1571", "1767", "2020", "2224", "2244", "2245", "2363", "452", "1402", "1893", "18", "38", "40", "46", "57", "64", "81", "82", "104", "107", "114", "121", "137", "142", "154", "197", "201", "252", "257", "260", "266", "286", "319", "325", "327", "343", "350", "357", "358", "410", "415", "455", "456", "465", "470", "471", "503", "504", "514", "773", "842", "1110", "1126", "1156", "1246", "1353", "1379", "1401", "1414", "1446", "1454", "1475", "1519", "1537", "1542", "1577", "1587", "1610", "1617", "1636", "1647", "1653", "1765", "1870", "1929", "1943", "1949", "1961", "1976", "2009", "2019", "2042", "2055", "2067", "2113", "2132", "2228", "2251", "2302", "2360", "2362")
)
```
```{r}
rootclones

```


```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_5, cells.highlight = rootclones, cols.highlight = "#FDDA0D", pt.size = 2, sizes.highlight = 2)
```

#FDDA0D



```{r}
data <- data.frame(
  category = c(0, 9, 2, 1, 11, 10, 50, 8, 17, 25, 18, 23, 30, 24,22),
  value1 = c(129, 125, 96, 57, 39, 35, 32, 26, 17, 17, 16, 15, 12, 7,1))
```

```{r}
ggplot(data, aes(x = factor(category), y = value1, fill = factor(category))) +
  geom_bar(stat = "identity") +
  labs(title = "Stacked Barplot",
       x = "Category",
       y = "Value") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
129, 125, 96, 57, 39, 35, 32, 26, 17, 17, 16, 15, 12, 7,1
```{r}
library(ggplot2)

# Example data
data <- data.frame(
  category = c("A"),  # Categories
  value1 = c(129),         # Values for the first segment
  value2 = c(125), 
  value3 = c(96), 
  value4 =c(57), 
  value5= c(39), 
  value6=c(35), 
  value7=c(32), 
  value8=c(26), 
  value9=c(17), 
  value10=c(17), 
  value11=c(16), 
  value12=c(15), 
  value13=c(12), 
  value14=c(7), 
  value15=c(1) # Values for the second segment
)

# Melt the data to long format
data_long <- reshape2::melt(data, id.vars = "category")

# Create stacked bar plot
ggplot(data_long, aes(x = category, y = value, fill = variable)) +
  geom_bar(stat = "identity") +
  labs(title = "Stacked Bar Plot Example",
       x = "Category",
       y = "Value",
       fill = "Segment") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



```
```{r}
library(ggplot2)

# Example data
data <- data.frame(
  category = c("A"),  # Categories
  value1 = c(129),         # Values for the first segment
  value2 = c(125), 
  value3 = c(96), 
  value4 =c(57), 
  value5= c(39), 
  value6=c(35), 
  value7=c(32), 
  value8=c(26), 
  value9=c(17), 
  value10=c(17), 
  value11=c(16), 
  value12=c(15), 
  value13=c(12), 
  value14=c(7), 
  value15=c(1) # Values for the second segment
)

# Melt the data to long format
data_long <- reshape2::melt(data, id.vars = "category")

# Create stacked bar plot with custom color coding
plotHC <- ggplot(data_long, aes(x = category, y = value, fill = variable)) +
  geom_bar(stat = "identity") +
  labs(title = "Stacked Bar Plot Example",
       x = "Category",
       y = "Value",
       fill = "Segment") +
  scale_fill_manual(values = c(
    "value1" =  "#7393B3",
    "value2" = "#CC5500",
    "value3" = "#6495ED",
    "value4" = "#0047AB",
    "value5" = "#4F7942",
    "value6" = "#F4C430",
    "value7" = "#89CFF0",
    "value8" = "#0096FF",
    "value9" = "#FFEA00",
    "value10" = "#FFAC1C",
    "value11" = "#009E60",
    "value12" = "#008000",
    "value13" = "#50C878",
    "value14" = "#097969",
    "value15" = "#FDDA0D"
  )) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
"8"  "50" "0"  "2"  "1"  "25" "9"  "18" "24" "30" "11" "23" "17" "22" "7"  "10" "16" "40" "60" "4"  "3"  "5"  "6"  "19"

```{r}
imPlot(Trex_mt10dim40_SCT_clone_sub2_5, cols=c(8 ="#0096FF", 50= "#89CFF0", 0= "#7393B3", 2 = "#6495ED", 1= "#0047AB", 25 ="#FFAC1C", 9 = "#CC5500", 18= "#009E60", 24 ="#097969", 30 ="#50C878", 11= "#4F7942", 23=  "#008000", 17 = "#FFEA00", 22 = "#FDDA0D", =7"#DAA520", 26 = "#DAA520", 51 = "#FDDA0D",  10 ="#F4C430", 16 = "#E4D00A", 40 ="#E0115F", "grey", "grey", 4 ="#E97451", 3= "#AA4A44", 5 =	"#E34234", 6 = "#E3735E", 19 = "black"
```


(0, 9, 2, 1, 11, 10, 50, 8, 17, 25, 18, 23, 30, 24,22)
```{r}
"#7393B3", "#CC5500", "#6495ED", "#0047AB", "#4F7942", "#F4C430", "#89CFF0", "#0096FF", "#FFEA00", "#FFAC1C", "#009E60", "#008000", "#50C878", "#097969", "#FDDA0D"
```

-- pie charts -- 

```{r}
pie_colors <- c("#3d85c6", "grey","#FFEA00", "#9F2B68", "#D22B2B")
```

```{r}
DimPlot(Trex_mt10dim40_SCT_clone_sub2_2, cells.highlight = list_barcodes, order = TRUE, cols.highlight = c("#D22B2B80", "#9F2B6880", "#FFEA0080", "#FFAC1C80", "#6495ED80"))
```



```{r}
data <- data.frame(
  group=LETTERS[1:2],
  value=c(59,41)
)

# Basic piechart
ggplot(data, aes(x="", y=value, fill=group)) + scale_fill_manual(values =pie_colors) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() 




```


